Negative Perceptions of Outsourcing to Artificial Intelligence

### 2025-06-23 appendix.qmd
Further edits for submission
Recreate manuscript as docx and submit

\vspace*{60mm}

@@

\setcounter{page}{1}
\begin{center}
Negative Perceptions of Outsourcing to Artificial Intelligence \\
AUTHORS REDACTED \\
AFFILIATION REDACTED
\end{center}
\newpage

# Pilot Study 1

@@

@@

We fitted a Bayesian multivariate multilevel cumulative-link ordinal model to 
the data using the *brms* R package. We modelled each task evaluation as a 
separate response variable and included correlated varying intercepts for
participants and tasks. We used regularising priors for all parameters to impose 
conservatism on parameter estimates (see Supplementary Materials for full model 
specification). The model converged normally ($\hat{R}$ ≤ 1.01).

@@

# Pilot Study 2

We conducted a power simulation to determine our target sample size. The 
simulation suggested that a sample size of 150 participants per condition 
(overall *n* = 450 for three conditions) would be required to detect a small 
difference between conditions (Cohen's *d* ≈ 0.20) with above 80% power.

```{r}
study1_sample <-
  tar_read(study1_data) %>%
  group_by(id) %>%
  summarise(
    gender = unique(gender),
    age = unique(age),
    chatgpt_used = unique(chatgpt_used)
    )
```

We recruited a convenience sample of 500 participants from the United Kingdom 
through Prolific. After excluding participants who failed our pre-treatment 
attention check, we were left with a final sample of 
`r nrow(study1_sample)` participants (`r sum(study1_sample$gender == "Female")`
female; `r sum(study1_sample$gender == "Male")` male;
`r sum(study1_sample$gender == "Non-binary / third gender")`
non-binary / third gender;
`r sum(str_starts(study1_sample$gender, "Prefer") | is.na(study1_sample$gender))`
undisclosed gender; mean age = `r round(mean(study1_sample$age), 2)` years).
`r round(mean(study1_sample$chatgpt_used == "Yes", na.rm = TRUE) * 100, 0)`% of
these participants reported having used ChatGPT before.

### Design

We randomly allocated participants into one of three conditions in a 
between-subjects design: (*i*) the control condition, (*ii*) the AI outsourcing
condition, or (*iii*) the human outsourcing condition. These conditions 
determined how scenarios were presented to participants.

We presented participants with six scenarios. Each scenario described a person 
completing a task, such as writing computer code or writing a love letter. The 
six tasks were randomly drawn from a larger set of 20 tasks (see @supptbl-tasks
for the full list of tasks). For each scenario, we told participants:

- *Control condition*: "In order to complete this task, [the person] works on it 
by themselves from start to finish."
- *AI outsourcing condition*: "In order to complete this task, [the person] gets
the AI tool ChatGPT to do it for them."
- *Human outsourcing condition*: "In order to complete this task, [the person]
gets someone else to do it for them."

We then asked participants how well each of the following words described the 
person in the scenario: competent, warm, moral, lazy, and trustworthy.
Participants answered these questions on 7-point Likert scales, ranging from 
"does not describe [the person] well" to "describes [the person] extremely well".

After the six scenarios, we asked participants several questions about the AI 
tool ChatGPT, including their familiarity with ChatGPT, whether they had used 
ChatGPT before, how frequently they used ChatGPT, and how trustworthy they 
thought ChatGPT was.

### Pre-registration

We pre-registered the study on the Open Science Framework
(<https://osf.io/xhmzk/?view_only=a4da193574d7410ba4d2aa3945a28b05>).

We fitted Bayesian multivariate multilevel cumulative-link ordinal models to the
data using the *brms* R package. We modelled each character evaluation -- 
competence, warmth, morality, laziness, and trustworthiness -- as a separate 
response variable and included fixed effects for conditions, varying intercepts
for participants, and varying intercepts and slopes for tasks. We used
regularising priors for all parameters to impose conservatism on parameter
estimates (see Supplementary Materials for full model specifications). All
models converged normally ($\hat{R}$ ≤ 1.01).

We found that people who outsourced tasks to AI or other humans were perceived 
more negatively than people who completed the tasks themselves 
(@suppfig-treatments-pilotstudy2). In particular, people who outsourced were 
perceived as lazier and less competent, with smaller yet detectable differences 
for perceptions of warmth, morality, and trustworthiness 
(@supptbl-treatment-diffs-pilotstudy2). Across all measures, outsourcing to 
other humans was perceived more negatively than outsourcing to AI.

We found that the effects of outsourcing varied across the different tasks, 
especially for perceptions of warmth and morality 
(@suppfig-treatments-by-task-pilotstudy2). For example, people were perceived as 
less warm if they outsourced writing a love letter, but not if they outsourced 
writing computer code. Similarly, people were perceived as less moral if they 
outsourced writing an apology letter to a friend, but not if they outsourced 
writing a dinner recipe. By contrast, the effects of outsourcing on competence, 
laziness, and trustworthiness were more consistent across tasks.

To determine the factors that predict variation across tasks, we incorporated
ratings of tasks from the first pilot study. Participants were asked to rate the 
20 tasks on several features: whether the task is social, requires social skills, 
impacts others, has important consequences, and requires effort. All of these 
features predicted stronger causal effects of outsourcing compared to control
(Supplementary Figures [-@suppfig-interactions-pilotstudy2] and 
[-@suppfig-interaction-pars-pilotstudy2]). In other words, outsourcing to AI or 
other humans is perceived more negatively for tasks that have these features, 
compared to tasks without these features.

# Vignette Wording in Study 5

:::{.NoIndent}
We presented participants in Study 5 with the following vignette text:
:::

@@

# Methods for Text Analysis in Study 5

To generate frequency lists for each experimental condition in Study 5, we 
created three documents containing the raw text submissions to the open-ended 
question "In your own words, describe how you feel about Adam and why". Each raw 
text submission was paired with a numbered text ID column. The number of 
submissions was roughly equivalent across conditions: the control condition (N = 
196), the tool outsourcing condition (N = 215), and the full outsourcing 
condition (N = 202).

@@

The impact of task-specific features (e.g., being a social task) on the causal
effects of outsourcing to AI compared to the control condition in Study 1. The 
y-axis reflects the estimated differences between the experimental conditions 
and the control condition (dashed line) on a 7-point Likert scale. Lines and 
shaded areas represent posterior medians and 95% credible intervals, 
respectively. The patterns indicate, for example, more negative effects of 
outsourcing on character evaluations for tasks that are rated as more social.

@@

Interaction parameters from models including task-specific features as
moderators of the causal effects of AI outsourcing compared to the control 
condition in Study 1. Points and line ranges represent posterior medians and 95% 
credible intervals, respectively.

@@

::: {#suppfig-treatments-person-study2 suppfig-pos="H"}

Character evaluations in Study 2. Participants in the control condition, the 
tool outsourcing condition, and the full outsourcing condition evaluated the 
"other participant" on (a) competence, (b) warmth, (c) morality, (d) laziness, 
and (e) trustworthiness. Jittered points represent participant responses to the
questions, split by whether the writing task was a non-social task (red) or a 
social task (blue). Point ranges are estimated marginal means from the fitted 
model, pooling over essay answers. Points and line ranges represent posterior 
medians and 95% credible intervals, respectively.

@@

::: {#suppfig-interactions-study3 suppfig-pos="H"}

The impact of task-specific features (e.g., being a social task) on the causal
effects of outsourcing to AI compared to the control condition in Study 3. The 
y-axis reflects the estimated differences between the experimental conditions 
and the control condition (dashed line) on a 7-point Likert scale. Lines and 
shaded areas represent posterior medians and 95% credible intervals, 
respectively. The patterns indicate, for example, more negative effects of 
outsourcing on character evaluations for tasks that are rated as more social.

@@

::: {#suppfig-interaction-pars-study3 suppfig-pos="H"}

Interaction parameters from models including task-specific features as
moderators of the causal effects of AI outsourcing compared to the control 
condition in Study 3. Points and line ranges represent posterior medians and 95% 
credible intervals, respectively.

@@

@@

::: {#suppfig-reasons-tasks-study4 suppfig-pos="H"}

@@

Variation in the effect of reasons across tasks in Study 4. Tasks are ordered 
from most social (top) to least social (bottom) according to ratings from a 
pilot study. Point ranges are differences in marginal means on a 7-point Likert 
scale between the "bad reason" and "good reason" conditions, split by 
outsourcing type. Points and ranges represent posterior medians and 95% credible 
intervals, respectively.

@@

Model-estimated task-specific correlations between all six questions in the 
first pilot study. Values are posterior median correlations. A positive 
correlation indicates that tasks that are rated highly on one question tend to 
be rated highly on another question.

@@

Model-estimated means for the question "Is this a social task?" across all 20 
tasks in the first pilot study. Grey points represent participant responses to 
the question, jittered for easier viewing. Black points are estimated means from
the fitted model, pooling over participants. Black points and line ranges 
represent posterior medians and 95% credible intervals, respectively.

@@

Model-estimated means for the question "Does this task require social skills?" 
across all 20 tasks in the first pilot study. Grey points represent participant 
responses to the question, jittered for easier viewing. Black points are 
estimated means from the fitted model, pooling over participants. Black points 
and line ranges represent posterior medians and 95% credible intervals, 
respectively.

@@

Model-estimated means for the question "Does this task impact other people?" 
across all 20 tasks in the first pilot study. Grey points represent participant 
responses to the question, jittered for easier viewing. Black points are 
estimated means from the fitted model, pooling over participants. Black points 
and line ranges represent posterior medians and 95% credible intervals,
respectively.

@@

Model-estimated means for the question "How important are the consequences of 
this task?" across all 20 tasks in the first pilot study. Grey points represent 
participant responses to the question, jittered for easier viewing. Black points
are estimated means from the fitted model, pooling over participants. Black
points and line ranges represent posterior medians and 95% credible intervals, 
respectively.

@@

Model-estimated means for the question "How important is it that effort goes 
into this task?" across all 20 tasks in the first pilot study. Grey points 
represent participant responses to the question, jittered for easier viewing.
Black points are estimated means from the fitted model, pooling over
participants. Black points and line ranges represent posterior medians and 95% 
credible intervals, respectively.

@@

Model-estimated means for the question "How important is it that others see the 
effort that goes into this task?" across all 20 tasks in the first pilot study.
Grey points represent participant responses to the question, jittered for easier 
viewing. Black points are estimated means from the fitted model, pooling over 
participants. Black points and line ranges represent posterior medians and 95% 
credible intervals, respectively.

::: {#suppfig-treatments-pilotstudy2 suppfig-pos="H"}

```{r, fig.height=4, fig.width=6}
tar_read(plot_treatments_study1)
```

Character evaluations in the second pilot study. Participants in the control 
condition, the AI outsourcing condition, and the human outsourcing condition 
evaluated people in the scenarios on (a) competence, (b) warmth, (c) morality,
(d) laziness, and (e) trustworthiness. Coloured points represent participant 
responses to the questions, jittered for easier viewing. Black points are 
estimated marginal means from the fitted model, pooling over participants and 
tasks. Black points and line ranges represent posterior medians and 95% credible 
intervals, respectively.

::: {#suppfig-treatments-by-task-pilotstudy2 suppfig-pos="H"}

```{r, fig.height=5, fig.width=8.5}
tar_read(plot_treatments_tasks_study1)
```

Variation in the effects of outsourcing across tasks in the second pilot study. 
Tasks are ordered from most social (top) to least social (bottom) according to 
ratings from the first pilot study. Point ranges are differences in marginal 
means on a 7-point Likert scale for the AI outsourcing condition (red) and 
the human outsourcing condition (blue) compared to the control condition. Points 
and ranges represent posterior medians and 95% credible intervals, respectively.

::: {#suppfig-interactions-pilotstudy2 suppfig-pos="H"}

The impact of task-specific features (e.g., being a social task) on the causal
effects of outsourcing to AI (red) and humans (blue) compared to the control
condition in the second pilot study. The y-axis reflects the estimated 
differences between the experimental conditions and the control condition 
(dashed line) on a 7-point Likert scale. Lines and shaded areas represent 
posterior medians and 95% credible intervals, respectively. The patterns 
indicate, for example, more negative effects of outsourcing on character 
evaluations for tasks that are rated as more social.

::: {#suppfig-interaction-pars-pilotstudy2 suppfig-pos="H"}

Interaction parameters from models including task-specific features as
moderators of the causal effects of AI outsourcing (red) and human outsourcing 
(blue) compared to the control condition in the second pilot study. Points and 
line ranges represent posterior medians and 95% credible intervals,
respectively.

@@

```{r}
tar_read(table_tasks) %>%
  kable(
    format = "latex",
    escape = FALSE,
    booktabs = TRUE,
    linesep = "",
    align = "lccccc"
  ) %>%
  kable_styling(font_size = 10)
```

@@

::: {#supptbl-essay-answers-social-study2 supptbl-pos="H" layout-ncol="1"}

```{r}
table <- 
  tar_read(table_essay_answers_study3) %>%
  slice(1:3) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 10) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "14cm")

# table single spaced
paste(
  "\\begingroup",
  "\\linespread{1}\\selectfont",
  table,
  "\\endgroup",
  sep = "\n"
  ) %>%
  knitr::asis_output()
```

Pre-generated essay answers to the social prompt in Study 2.

@@

::: {#supptbl-essay-answers-nonsocial-study2 supptbl-pos="H" layout-ncol="1"}

```{r}
table <- 
  tar_read(table_essay_answers_study3) %>%
  slice(4:6) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 10) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "14cm")

# table single spaced
paste(
  "\\begingroup",
  "\\linespread{1}\\selectfont",
  table,
  "\\endgroup",
  sep = "\n"
  ) %>%
  knitr::asis_output()
```

Pre-generated essay answers to the non-social prompt in Study 2.

::: {#supptbl-essay-comprehension-study2 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_essay_comprehension_study3) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 9)
```

Reading times and comprehension rates for the essay answers in Study 2. Expected
reading times were calculated based on an estimated reading speed of 275 words
per minute. Comprehension rates are the percentage of participants who answered
the comprehension question correctly.

::: {#supptbl-manipulation-check-study2 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_manipulation_check_study3) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 11)
```

Percentage of participants in Study 2 who passed the manipulation check and 
reported that they believed the manipulation, split by condition.

::: {#supptbl-treatment-diffs-person-study2 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_treatment_diffs_effects_study3) %>%
  dplyr::select(c(1, 7:11)) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 7.5) %>%
  add_header_above(header = c(" " = 1, "Response" = 5)) %>%
  pack_rows(
    index = c(
      "Effect of outsourcing type" = 6,
      "Effect of task type" = 3,
      "Interaction effect" = 3
      )
    ) %>%
  pack_rows("\u00A0\u00A0Task type = Social", 1, 3, indent = FALSE) %>%
  pack_rows("\u00A0\u00A0Task type = Non-social", 4, 6, indent = FALSE)
```

Pairwise contrasts for character evaluations in Study 2. Numbers reflect 
differences in marginal means on a 7-point Likert scale. Estimates are pooled 
over essay answers. The bottom rows represent the interactions between 
outsourcing type and task type. Main numbers are posterior medians, numbers in 
the square brackets are 95% credible intervals.

@@

::: {#supptbl-text-analysis-study5 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_text_analysis_study6) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 8)
```

Pairwise comparisons of word frequencies between conditions. LL = log 
likelihood.

@@

::: {#supptbl-treatment-diffs-pilotstudy2 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_treatment_diffs_study1) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    linesep = ""
  ) %>%
  kable_styling(font_size = 9) %>%
  add_header_above(header = c(" " = 1, "Response" = 5))
```

Pairwise contrasts in the second pilot study. Numbers reflect differences in 
marginal means on a 7-point Likert scale, pooling over participants and tasks. 
Main numbers are posterior medians, numbers in the square brackets are 95% 
credible intervals.

@@

@@

\setlength{\parindent}{-20pt}
\setlength{\leftskip}{20pt}

>>>>

@@

# Pilot Study

@@

<br>

@@

We fitted a Bayesian multivariate multilevel cumulative-link ordinal model to
the data using the *brms* R package. We modelled each task evaluation as a
separate response variable and included correlated varying intercepts for
participants and tasks. We used regularizing priors for all parameters to impose
conservatism on parameter estimates (see Supplementary Materials for full model
specification). The model converged normally ($\hat{R}$ ≤ 1.01).

@@

# Vignette Wording in Study 6

:::{.NoIndent}
We presented participants in Study 6 with the following vignette text:
:::

@@

# Methods for Text Analysis in Study 6

To generate frequency lists for each experimental condition in Study 6, we
created three documents containing the raw text submissions to the open-ended
question "In your own words, describe how you feel about Adam and why". Each raw
text submission was paired with a numbered text ID column. The number of
submissions was roughly equivalent across conditions: the control condition (N =
196), the tool outsourcing condition (N = 215), and the full outsourcing
condition (N = 202).

@@

The impact of task-specific features (e.g., being a social task) on the causal
effects of outsourcing to AI (red) and humans (blue) compared to the control
condition in Study 1. The y-axis reflects the estimated differences between the 
experimental conditions and the control condition (dashed line) on a 7-point 
Likert scale. Lines and shaded areas represent posterior medians and 95% 
credible intervals, respectively. The patterns indicate, for example, more 
negative effects of outsourcing on character evaluations for tasks that are 
rated as more social.

@@

Interaction parameters from models including task-specific features as
moderators of the causal effects of AI outsourcing (red) and human outsourcing
(blue) compared to the control condition in Study 1. Points and line ranges 
represent posterior medians and 95% credible intervals, respectively.

@@

::: {#suppfig-interactions-study2 suppfig-pos="H"}

The impact of task-specific features (e.g., being a social task) on the causal
effects of outsourcing to AI compared to the control condition in Study 2. The
y-axis reflects the estimated differences between the experimental conditions
and the control condition (dashed line) on a 7-point Likert scale. Lines and
shaded areas represent posterior medians and 95% credible intervals,
respectively. The patterns indicate, for example, more negative effects of
outsourcing on character evaluations for tasks that are rated as more social.

@@

::: {#suppfig-interaction-pars-study2 suppfig-pos="H"}

Interaction parameters from models including task-specific features as
moderators of the causal effects of AI outsourcing compared to the control
condition in Study 2. Points and line ranges represent posterior medians and 95%
credible intervals, respectively.

@@

::: {#suppfig-treatments-person-study3 suppfig-pos="H"}

Character evaluations in Study 3. Participants in the control condition, the
tool outsourcing condition, and the full outsourcing condition evaluated the
"other participant" on (a) competence, (b) warmth, (c) morality, (d) laziness,
and (e) trustworthiness. Jittered points represent participant responses to the
questions, split by whether the writing task was a non-social task (red) or a
social task (blue). Point ranges are estimated marginal means from the fitted
model, pooling over essay answers. Points and line ranges represent posterior
medians and 95% credible intervals, respectively.

@@

::: {#suppfig-interactions-study5 suppfig-pos="H"}

The impact of task-specific features (e.g., being a social task) on the causal
effects of outsourcing to AI compared to the control condition in Study 5. The
y-axis reflects the estimated differences between the experimental conditions
and the control condition (dashed line) on a 7-point Likert scale. Lines and
shaded areas represent posterior medians and 95% credible intervals,
respectively. The patterns indicate, for example, more negative effects of
outsourcing on character evaluations for tasks that are rated as more social.

::: {#suppfig-interaction-pars-study5 suppfig-pos="H"}

Interaction parameters from models including task-specific features as
moderators of the causal effects of AI outsourcing compared to the control
condition in Study 5. Points and line ranges represent posterior medians and 95%
credible intervals, respectively.

@@

::: {#suppfig-reasons-tasks-study5 suppfig-pos="H"}

@@

Variation in the effect of reasons across tasks in Study 5. Tasks are ordered
from most social (top) to least social (bottom) according to ratings from a
pilot study. Point ranges are differences in marginal means on a 7-point Likert
scale between the "bad reason" and "good reason" conditions, split by
outsourcing type. Points and ranges represent posterior medians and 95% credible
intervals, respectively.

@@

Model-estimated task-specific correlations between all six questions in the
pilot study. Values are posterior median correlations. A positive correlation 
indicates that tasks that are rated highly on one question tend to be rated 
highly on another question.

@@

Model-estimated means for the question "Is this a social task?" across all 20
tasks in the pilot study. Grey points represent participant responses to
the question, jittered for easier viewing. Black points are estimated means from
the fitted model, pooling over participants. Black points and line ranges
represent posterior medians and 95% credible intervals, respectively.

@@

Model-estimated means for the question "Does this task require social skills?"
across all 20 tasks in the pilot study. Grey points represent participant
responses to the question, jittered for easier viewing. Black points are
estimated means from the fitted model, pooling over participants. Black points
and line ranges represent posterior medians and 95% credible intervals,
respectively.

@@

Model-estimated means for the question "Does this task impact other people?"
across all 20 tasks in the pilot study. Grey points represent participant
responses to the question, jittered for easier viewing. Black points are
estimated means from the fitted model, pooling over participants. Black points
and line ranges represent posterior medians and 95% credible intervals,
respectively.

@@

Model-estimated means for the question "How important are the consequences of
this task?" across all 20 tasks in the pilot study. Grey points represent
participant responses to the question, jittered for easier viewing. Black points
are estimated means from the fitted model, pooling over participants. Black
points and line ranges represent posterior medians and 95% credible intervals,
respectively.

@@

Model-estimated means for the question "How important is it that effort goes
into this task?" across all 20 tasks in the pilot study. Grey points
represent participant responses to the question, jittered for easier viewing.
Black points are estimated means from the fitted model, pooling over
participants. Black points and line ranges represent posterior medians and 95%
credible intervals, respectively.

@@

Model-estimated means for the question "How important is it that others see the
effort that goes into this task?" across all 20 tasks in the pilot study.
Grey points represent participant responses to the question, jittered for easier
viewing. Black points are estimated means from the fitted model, pooling over
participants. Black points and line ranges represent posterior medians and 95%
credible intervals, respectively.

@@

```{r}
tar_read(table_tasks) %>%
  flextable() %>%
  theme_apa() %>%
  width(width = c(3, rep(1, 5))) %>%
  line_spacing() %>%
  align(i = NULL, j = 1, align = "left", part = "all")
```

@@

@@

@@

::: {#supptbl-essay-answers-social-study3 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_essay_answers_study3) %>%
  slice(1:3) %>%
  flextable() %>%
  theme_apa() %>%
  width(width = c(1, 8)) %>%
  line_spacing() %>%
  align(i = NULL, j = NULL, align = "left", part = "all")
```

Pre-generated essay answers to the social prompt in Study 3.

@@

::: {#supptbl-essay-answers-nonsocial-study3 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_essay_answers_study3) %>%
  slice(4:6) %>%
  flextable() %>%
  theme_apa() %>%
  width(width = c(1, 8)) %>%
  line_spacing() %>%
  align(i = NULL, j = NULL, align = "left", part = "all")
```

Pre-generated essay answers to the non-social prompt in Study 3.

@@

::: {#supptbl-essay-comprehension-study3 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_essay_comprehension_study3) %>%
  flextable() %>%
  theme_apa() %>%
  autofit()
```

Reading times and comprehension rates for the essay answers in Study 3. Expected
reading times were calculated based on an estimated reading speed of 275 words
per minute. Comprehension rates are the percentage of participants who answered
the comprehension question correctly.

::: {#supptbl-manipulation-check-study3 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_manipulation_check_study3) %>%
  flextable() %>%
  theme_apa() %>%
  autofit()
```

Percentage of participants in Study 3 who passed the manipulation check and
reported that they believed the manipulation, split by condition.

::: {#supptbl-treatment-diffs-person-study3 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_treatment_diffs_effects_study3) %>%
  dplyr::select(c(1, 7:11)) %>%
  mutate(
    group = c(
      rep("Effect of outsourcing type (Task type = Social)", 3),
      rep("Effect of outsourcing type (Task type = Non-social)", 3),
      rep("Effect of task type", 3),
      rep("Interaction effect", 3)
    )
  ) %>%
  as_grouped_data(groups = "group") %>%
  as_flextable(hide_grouplabel = TRUE) %>%
  theme_apa() %>%
  width(width = c(2, rep(1.5, 5))) %>%
  bold(i = ~ !is.na(group)) %>%
  add_header_row(values = c("", "Response"), colwidths = c(1, 5)) %>%
  align(i = 1, j = NULL, align = "center", part = "header") %>%
  align(i = NULL, j = 1, align = "left", part = "all") %>%
  line_spacing() %>%
  fontsize(size = 8)
```

Pairwise contrasts for character evaluations in Study 3. Numbers reflect
differences in marginal means on a 7-point Likert scale. Estimates are pooled
over essay answers. The bottom rows represent the interactions between
outsourcing type and task type. Main numbers are posterior medians, numbers in
the square brackets are 95% credible intervals.

::: {#supptbl-text-analysis-study6 supptbl-pos="H" layout-ncol="1"}

```{r}
tar_read(table_text_analysis_study6) %>%
  flextable() %>%
  theme_apa() %>%
  autofit()
```

Pairwise comparisons of word frequencies between conditions in Study 6. LL = log
likelihood.

@@
